A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-23 paper/paper.tex
paper: fix one paragraph

There are a few more subtleties. In $\cohf$ and $\cohc$, we use the reflection rule to identify equalities of pairs with a conjunction of two equalities. In $\cohl$, we use the reflection rule to identify equality of functions with point-wise equality. We additionally rely heavily on basic properties of the groupoid transport, which we don't detail.

@@

Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences. For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U. See \cite{herbelin15,altenkirch16,kraus21} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.

@@

By placing the definition in \SProp, we have definitional equality of all inequality proofs. For the purpose of unification, however, this definition does not go far enough. Consider the unification problems:

\begin{minted}{coq}
  le_trans ?p le_refl = ?p
  le_trans le_refl ?p = ?p
\end{minted}
where \texttt{le\_trans} is transitivity, \texttt{le\_refl} is reflexivity, and \texttt{?p} is an existential variable. These two problems definitionally hold in \SProp, but equalizing them does not solve the existential. For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':

@@

\texttt{leY} is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral element of transitivity, and associativity of transitivity also holds definitionally. Although it significantly eases our proof, there are some instances where unification is unable to solve for the existentials, and we have to provide them explicitly.

>>>>

Like in \ref{tab:coh}, we leave implicit in \ref{fulltab:coh}, the use of the isomorphism between the type of equalities of dependent pairs in a $\Sigma$-type with the $\Sigma$-type of equalities of the components of the pair, as well as the isomorphism between equality of functions with point-wise equality. Contrary to the ETT case, functional extensionality does not hold, so we assume it. However, the requirement of functional extensionality disappears if $\nu$ is finite. As for basic groupoid properties of equalities, which no longer hold definitionally, we do not mention them for simplicity.

@@

Remark: If we were not working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences. For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U. See \cite{herbelin15,altenkirch16,kraus21} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.

@@

Here \SProp is a definitionally proof-irrelevant impredicative universe at the bottom of the universe hierarchy~\cite{gilbert19}. By placing the definition in \SProp, we have definitional equality of all inequality proofs. For the purpose of unification, however, this definition does not go far enough. Consider the unification problems:

\begin{minted}{coq}
  leR_trans ?p leR_refl = ?p
  leR_trans leR_refl ?p = ?p
\end{minted}
where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable. These two problems definitionally hold in \SProp, but equalizing them does not solve the existential. For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':

@@

This definition is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral element of transitivity, and associativity of transitivity also holds definitionally. Although it significantly eases our proof, there are some instances where unification is unable to solve the existentials, and we have to provide them explicitly.
